Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
checkpoint through 5.2

  &
  & 10,000
  & (DJBDNS) \\

\cc{unzip}
  & 220
  & 1600
  & (Info-Zip) \\
\bottomrule
\end{tabular}
\caption{Comparison of code size for three applications written in Nail,
         and several existing alternative implementations.}
\label{fig:effort}
\end{figure}

@@

It is hard to compare the programming effort required to implement
our DNS server to that of a real world DNS server, since we implement
less functionality: we do not send the additional glue records and
we did not implement any configuration options.  However, the closest
in functionality and intent is Dan Bernstein's djbdns~\cite{djbdns},
which aims to be a minimalist, highly secure, authoritative-only DNS
server. The latest release of djbdns, including various support tools,
is about 10,000 lines of C\@.  \XXX[nz][so what does this mean?]

@@

We wrote a grammar for ZIP, which consists of 92 lines of Nail and 78 lines of C implementing two
stream transforms, one for the DEFLATE compression algorithm with the help of the zlib library and
one for finding the end-of-directory header.

Our grammar is also very efficient to use. Using our grammar, we build a ZIP file extractor in 50
lines of C. Because more recent versions of ZIP have added more features, such as large file support
and encryption, the closest existing tool in functionality is the historic version 5.4 of the Info-Zip unzip
utility\cite{infozip} that is shipped with most Linux distributions. The entire unzip distribution
is about 46.000 lines of code, which is mostly optimized implementation of various compression
algorithms and other configuration and portability code.

However, unzip isolates the equivalent of our Nail tool in the file extract.c, which parses the ZIP
metadata and calls various decompression routines in other files. This file measures over 1,600
lines of C.

\subsection{Security.} 
We use a twofold approach to evaluate the security of applications implemented with Nail. First, we
analyze a list of CVE's related to the ZIP file format and argue how our ZIP tools based on Nail are
immune against those vulnerability classes. Second, we present the results of fuzz-testing our DNS
server.

@@

To provide additional assurance that Nail parsers are free of memory corruption attacks, we ran the
DNS fuzzer provided with the Metasploit\cite{mspframework} framework on our server, which sent
randomly corrupted DNS queries to our server for 4 hours, during which it did not crash or trigger
the stack or heap corruption detector.
\subsection{Performance.}
\input{fig-perf-dns}
To estimate the performance impact of using Nail grammars as opposed to hand-written grammars, we
benchmarked our DNS server against BIND.

>>>>

%  &
%  & 10,000
%  & (DJBDNS) \\

\cc{unzip}
  & 220
  & 1,600
  & (Info-Zip) \\
\bottomrule
\end{tabular}
\caption{Comparison of code size for three applications written in Nail,
         and several existing alternative implementations.}
\label{fig:effort}
\end{figure}

@@

% It is hard to compare the programming effort required to implement
% our DNS server to that of a real world DNS server, since we implement
% less functionality: we do not send the additional glue records and
% we did not implement any configuration options.  However, the closest
% in functionality and intent is Dan Bernstein's djbdns~\cite{djbdns},
% which aims to be a minimalist, highly secure, authoritative-only DNS
% server. The latest release of djbdns, including various support tools,
% is about 10,000 lines of C\@.  \XXX[nz][so what does this mean?]

@@

We implemented a ZIP file extractor in 50 lines of C code, together with
92 lines of Nail grammar and 78 lines of C code implementing two stream
transforms (one for the DEFLATE compression algorithm with the help of
the zlib library, and one for finding the end-of-directory header).

Because more recent versions of ZIP have added more features, such
as large file support and encryption, the closest existing tool
in functionality is the historic version 5.4 of the Info-Zip unzip
utility~\cite{infozip} that is shipped with most Linux distributions.
The entire unzip distribution is about 46,000 lines of code, which is
mostly optimized implementations of various compression algorithms and
other configuration and portability code.  However, unzip isolates the
equivalent of our Nail tool in the file \cc{extract.c}, which parses the
ZIP metadata and calls various decompression routines in other files. This
file measures over 1,600 lines of C, which suggests that Nail is highly
effective at reducing manual input parsing code, even for the complex
ZIP file format.

\subsection{Security}

We use a twofold approach to evaluate the security of applications implemented with Nail. First, we
analyze a list of CVE's related to the ZIP file format and argue how our ZIP tools based on Nail are
immune against those vulnerability classes. Second, we present the results of fuzz-testing our DNS
server.

@@

To provide additional assurance that Nail parsers are free of memory corruption attacks, we ran the
DNS fuzzer provided with the Metasploit\cite{mspframework} framework on our server, which sent
randomly corrupted DNS queries to our server for 4 hours, during which it did not crash or trigger
the stack or heap corruption detector.

\subsection{Performance}

To estimate the performance impact of using Nail grammars as opposed to hand-written grammars, we
benchmarked our DNS server against BIND.

\input{fig-perf-dns}
